\documentclass[12pt,-letter paper]{article}                           \usepackage{gvv}
\begin{document}
\begin{enumerate}
	\item Real numbers $a_1, a_2, \dots, a_n$ are g    iven. For each $i(1 \leq i \leq n)$ define \\
$d_i=max \{a_j : 1 \leq j \leq i\}$ - $min\{a_j : i \leq j \leq n\}$ and let \\
$d = max\{d_i : 1 \leq i \leq n\}$.\\
 \brak a Prove that, for any real numbers $x_1 \leq x_2 \leq \dots \leq x_n$, \\
$\{ | x_i - a_i | : 1 \leq  i \leq n \} \geq$  $\frac {d}{2}$. \brak * \\
\brak b Show that there are real numbers $x_1 \    leq x_2 \leq \dots \leq x_n$ such that equality     holds in \brak *.
\item Consider five points $A,B,C,D$ and $E$ such that $ABCD$ is a parallelogram and $BCED$ is a cycle quadrilateral.Let $l$ be a line passing through A. suppose that $l$ intersts the interior of the segment $DC$ at $F$ and intersects line $BC$ at $G$.suppose also that $EF=EG=EC$. Prove that $l$ is the bisector of angle $DAB$.
\item In a mathematical compentition some competitors are friends. Friendship is always mutual. Call a group of competitors a clique if each two of tem are friends. (In particular, any group of fewer than two competitors is a clique.) The number of members of a clique is called its size.
	Given that, in this competition, the largest size of a clique is even, prove that the competitors can be arranged in two rooms such that the largest size of a clique contained in one room is the same as the largest size of a clique contained in the other room.
\item In triangle $ABC$ the bisector of angle $BCA$ intersects the circumcircle again at $R$, the perpendicular bisector of $BC$ at $P$, and the perpendicular bisector of $AC$ at $Q$. The midpoint of $BC$ is $K$ and the midpoin of $AC$ is $L$.Prove that the triangles $RPK$ and $RQL$ have the same area.
\item Let $a and b$ be positive integers. Show that if $4ab-1$ divides $(4a^2-1)^2$, then $a=b$.
\item Let $n$ be a positive integer. Consider
	$S={(x,y,z)} : {x,y,z} \epsilon i{0,1,\dot,n}$, ${x+y+z>0}$ 
		as a set of $(n+1)^{3}-1$ points in three-dimensional space.Determine the smallest possible umber of planes, the union of which contains $S$ but does not include $(0,0,0)$.
\end{enumerate}
\end{document}









